---
title: "Prostate Path Parsing"
subtitle: "Comparison of Output"
author: "Anobel Y. Odisho, Mark Bridge, Matthew R. Cooperberg"
date: "`r Sys.Date()`"
output:
      html_document
      # tufterhandout::html_tufte_handout:
      # theme: cosmo
      # css: floating.css
      # toc: no

---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.width = 12, cache = F)
```


```{r}
# load packages
# library(dplyr)
library(knitr)

# load data
load(file="data/tidy/pp.rda")

```

# To Do
- can Mark re-extract data file that Matt gave me? we should pick up a lot more SDEs and parsed path reports, then can go through and abstract manually to confirm, update into UODB
- is there a data dictionary?
- if errors, feed back to mark to update regualr expressions
- path node status from UODB and SDE is all missing

# Gleason

## Available Data

make a table of available/missing values for u, p, s, prim, secondary

```{r}
# use dplyr and lapply to make table of missing values for primary/gleason by all u, p, s
# pp %>%
#   select(endsWith(gprimp), endsWith(gsecondp)) %>%
#   summary(is.na()) %>%
#   table() %>%
#   kable()

```

## Missing Data
- make cross tabs of missing data...betwen U, P, S, primary and secondary
- which is my gold standard? U? then it should be the most complete
- if available as SDE and parsed path, and missing in UODB, then should be manually entered

```{r}


```