---
title: "Prostate Path Parsing"
subtitle: "Comparison of Output"
author: "Data Date: 2017-10-15"
date: "Report Date: `r Sys.Date()`"
output: 
  tufterhandout::html_tufte_handout:
        theme: cosmo
        toc: true
        toc_float: true
        toc_depth: 2
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.width = 12, cache = F)
```


```{r, cache = F}
# load packages
library(dplyr)
library(tidyr)
library(knitr)
library(pander)
library(stargazer)
library(DT)
library(irr)
library(rel) #for correlation analysis

# load data
load(file="data/tidy/pp.rda")

# Create empty list to hold results
r <- list()

# Define the variables for which I want to do comparisons
vars <- c("glcombined", 
          "pathmgnpos", "pathecepos", "pathsvipos", 
          "pathnodes_dissected", "pathnodes_positive", "pathnodes_status",
          "tstagep", "nstagep")

# categorical variables
catvars <- c("glcombined", 
          "pathmgnpos", "pathecepos", "pathsvipos", 
          "pathnodes_status", "tstagep", "nstagep")

# continuous variables
contvars <- c("pathnodes_dissected", "pathnodes_positive")

```


```{r functions}
# Function to compare 2 data types against each other
compare2 <- function(x, y, varname) {
  # x is the first data source that will be used in the comparison
  # y is the first data source that will be used in the comparison
  # varname represents variables to compare
  x_compare <- paste0(x,"_",varname)
  y_compare <- paste0(y,"_",varname)
  
  total <- sum(!is.na(pp[,x_compare] == pp[,y_compare]))
  correct <- sum(pp[,x_compare] == pp[,y_compare], na.rm=T)

  result <- c(
    sprintf("%.0f",total), 
    sprintf("%.1f%%", (correct/total)*100)
  )
  m <- matrix(result, 1, 2)
  colnames(m) <- c(paste(x,"vs.", y, "(n)"),paste(x,"vs.", y, "(%)"))
  rownames(m) <- varname
  return(m)
}


# Function to compare all 3 data types against each other
compare3 <- function(varname) {
  # y represents variables to compare
  p_compare <- paste0("p_",varname)
  s_compare <- paste0("s_",varname)
  u_compare <- paste0("u_",varname)
  total <- sum(!is.na(pp[,u_compare]) & !is.na(pp[,s_compare]) & !is.na(pp[,p_compare]))
  correct <- sum(pp[,u_compare] == pp[,s_compare] & pp[,u_compare] == pp[,p_compare], na.rm = T)
  result <- c(
    sprintf("%.0f",total), 
    sprintf("%.1f%%", (correct/total)*100)
  )
  m <- matrix(result, 1, 2)
  colnames(m) <- c("All 3 (n)","All 3 (%)")
  rownames(m) <- varname
  return(m)
}

# Functiomn to make wide table of comparisons
allcomparisons <- function(x) {
  cbind(
    compare2("u", "p", x),
    compare2("u", "s", x),
    compare2("p", "s", x),
    compare3(x)
  )  
}

crosstables <- function(varname) {
  p_compare <- paste0("p_",varname)
  s_compare <- paste0("s_",varname)
  u_compare <- paste0("u_",varname)
  t <- list()
  t$t1 <- table(!is.na(pp[,p_compare]), !is.na(pp[,u_compare]), dnn=c("Parser", "UODB"))
  t$t2 <- table(!is.na(pp[,s_compare]), !is.na(pp[,u_compare]), dnn=c("SDE", "UODB"))
  t$t3 <- table(!is.na(pp[,s_compare]), !is.na(pp[,p_compare]), dnn=c("SDE", "Parser"))
  
  t$t4 <- table(pp[,p_compare], pp[,u_compare], dnn=c("Parser", "UODB"), useNA = "always")
  t$t5 <- table(pp[,s_compare], pp[,u_compare], dnn=c("SDE", "UODB"), useNA = "always")
  t$t6 <- table(pp[,s_compare], pp[,p_compare], dnn=c("SDE", "Parser"), useNA = "always")  
  
  return(t)
}

# this function calculates how often parser and SDE had exact same result
# but were incorrect compared to UODB

compareqc <- function(varname) {
  # varname represents variables to compare
  u_compare <- paste0("u_",varname)
  s_compare <- paste0("s_",varname)
  p_compare <- paste0("p_",varname)

  nomiss <- !is.na(pp[,u_compare]) & !is.na(pp[,s_compare]) & !is.na(pp[,p_compare])
  
  total <- sum(!is.na(pp[,u_compare] == pp[,s_compare]) & !is.na(pp[,u_compare] == pp[,p_compare]))
  
  correct <- total - sum(pp[nomiss,p_compare] == pp[nomiss,s_compare] & pp[nomiss, p_compare] != pp[nomiss, u_compare], na.rm = T)

  result <- c(
    sprintf("%.0f",total), 
    sprintf("%.1f%%", (correct/total)*100)
  )
  m <- matrix(result, 1, 2)
  colnames(m) <- c("(n)", "(%)")
  rownames(m) <- varname
  return(m)
}

```

# Available Data

- Total records: `r nrow(pp)`

## All Variables
```{r}
data.frame(
            "Variable" = colnames(pp),
            "Values Present" = apply(pp, 2, function(x) sum(!is.na(x))),
            "Data Present Percent" = apply(pp, 2, function(x) round((sum(!is.na(x))/nrow(pp))*100,2)),
            row.names = NULL
            ) %>% datatable()
```

# All Comparisons
```{r}
t <- lapply(vars, allcomparisons)
t <- do.call(rbind, t)

kable(t)
```

# Correlation Coefficients

```{r}
raters <- c("u", "s", "p")

catvargrid <- expand.grid(raters, catvars)
catvargrid <- paste0(catvargrid[,1], "_", catvargrid[,2])

# gleason comparisons
combo2 <- combn(names(pp[,catvargrid[1:3]]),2, simplify = F)
combo3 <- combn(names(pp[,catvargrid[1:3]]),3, simplify = F)

combo2
lapply(1:3, function(x) ckap(pp[combo2[[x]]]))

spi(pp[combo3[[1]]])

# path margin positive comparisons
combo2 <- combn(names(pp[,catvargrid[4:6]]),2, simplify = F)
combo3 <- combn(names(pp[,catvargrid[4:6]]),3, simplify = F)

combo2
lapply(1:3, function(x) ckap(pp[combo2[[x]]]))

spi(pp[combo3[[1]]])

# Path ECE positive
combo2 <- combn(names(pp[,catvargrid[7:9]]),2, simplify = F)
combo3 <- combn(names(pp[,catvargrid[7:9]]),3, simplify = F)

combo2
lapply(1:3, function(x) ckap(pp[combo2[[x]]]))

spi(pp[combo3[[1]]])

# Path SVI positive
combo2 <- combn(names(pp[,catvargrid[10:12]]),2, simplify = F)
combo3 <- combn(names(pp[,catvargrid[10:12]]),3, simplify = F)

combo2
lapply(1:3, function(x) ckap(pp[combo2[[x]]]))

spi(pp[combo3[[1]]])

# t stage
combo2 <- combn(names(pp[,catvargrid[16:18]]),2, simplify = F)
combo3 <- combn(names(pp[,catvargrid[16:18]]),3, simplify = F)

combo2
lapply(1:3, function(x) ckap(pp[combo2[[x]]]))

spi(pp[combo3[[1]]])

# N stage
combo2 <- combn(names(pp[,catvargrid[19:21]]),2, simplify = F)
combo3 <- combn(names(pp[,catvargrid[19:21]]),3, simplify = F)

combo2
lapply(1:3, function(x) ckap(pp[combo2[[x]]]))

spi(pp[combo3[[1]]])

# continuous variables
contvargrid <- expand.grid(raters, contvars)
contvargrid <- paste0(contvargrid[,1], "_", contvargrid[,2])

# nodes dissected
combo2 <- combn(names(pp[,contvargrid[1:3]]),2, simplify = F)
combo3 <- combn(names(pp[,contvargrid[1:3]]),3, simplify = F)

combo2

lapply(1:3, function(x) icc(pp[combo2[[x]]]))

icc(pp[combo3[[1]]])

# nodes positive
combo2 <- combn(names(pp[,contvargrid[4:6]]),2, simplify = F)
combo3 <- combn(names(pp[,contvargrid[4:6]]),3, simplify = F)

combo2
lapply(1:3, function(x) icc(pp[combo2[[x]]]))

icc(pp[combo3[[1]]])

pp$p_pathnodes_positive <- as.integer(pp$p_pathnodes_positive)



```

``` {r eval = F}
t <- cohen.kappa(pp[,combo2[[1]]])
combo2[[1]]
t



kappa()
pp[,c("u_glcombined", "p_glcombined")]
kappa()
str(v[[1]])

kappam.fleiss(pp[combo3[[1]]])

pp[combo3[[1]]]

cohen.kappa(pp[combo3[[1]]], all=T)
?cohen.kappa
ratings <- matrix(rep(1:5,4),ncol=4)
ratings[1,2] <- ratings[2,3] <- ratings[3,4] <- NA
ratings[2,1] <- ratings[3,2] <- ratings[4,3] <- 1

cohen.kappa(ratings)
    
?psych


t <- 
  



?kappa2
kappa()
summary(v[[1]])

r_glcombined <- pp %>% select(contains("glcombined"))

kappaCohen(r_glcombined)

tocheck <- combn(rownames(r_glcombined), 2, simplify = F)
names(tocheck) <- sapply(tocheck, paste, collapse = " - ")



raters <- c("u", "s", "p")
ratercombo <- combn(raters, 2, simplify = F)


paste0(ratercombo, "_", catvars)

kappa2()


```

# Gleason
```{r}
glreport <- data.frame(
  Category = c(
    "Complete cases from UODB", 
    "Complete cases from SDE",
    "Complete cases from Parser",
    "Complete cases from UODB and SDE",
    "Complete cases from UODB and Parser",
    "Complete cases from Parser and SDE",
    "Complete cases from UODB, SDE, Parser"
  ),
  Gleason = c(
    sum(!is.na(pp$u_glcombined)),
    sum(!is.na(pp$s_glcombined)),
    sum(!is.na(pp$p_glcombined)),
    sum(!is.na(pp$u_glcombined) & !is.na(pp$s_glcombined)),
    sum(!is.na(pp$u_glcombined) & !is.na(pp$p_glcombined)),
    sum(!is.na(pp$p_glcombined) & !is.na(pp$s_glcombined)),
    sum(!is.na(pp$u_glcombined) & !is.na(pp$s_glcombined) & !is.na(pp$p_glcombined))
  )
)

kable(glreport)

crosstables("glcombined")
```

# T Stage
```{r}
crosstables("tstagep")
```

# N Stage
```{r}
crosstables("tstagep")
```

# Path Margin Positive
```{r}
pp %>%
  filter(p_pathmgnpos_wmiss == 'Missing') %>%
  select(u_pathmgnpos, s_pathmgnpos, p_pathmgnpos_wmiss, p_pathmgnpos_raw) %>%
  kable() 



crosstables("pathmgnpos")

```

# Path ECE Positive
```{r, eval = F}
pp %>%
  filter(p_pathecepos_wmiss == 'Missing') %>%
  select(u_pathecepos, s_pathecepos, p_pathecepos_wmiss, p_pathecepos_raw) %>%
  kable()

crosstables("pathecepos")

```

# Path SVI Positive
```{r, eval=F}
pp %>%
  filter(p_pathsviepos == 'Missing') %>%
  select(u_pathsvipos, s_pathsvipos, p_pathsvipos, p_pathsvipos_raw) %>%
  kable()


crosstables("pathsvipos")
```

# Path Nodes Positive
```{r, eval = F}
crosstables("pathnodes_positive")
```

# Path Nodes Dissected
```{r, eval = F}
# crosstables("pathnodes_dissected")
```

# Quality Control Cases

Need to evaluate the number of cases in which the parser and the SDE had the same result, but were both wrong compared the gold standard, UODB

## Gleason Mismatch

- 1 case
- case row 1299
- Parser and SDE both read 3+4, UODB reads 3+3
- path report says, "3+4=7; primary pattern 3, secondary pattern 3."

## Path ECE Mismatch

- 1 case
- case row 1767
- Path report reads, "Focal, positive". Parser called it positive. SDE entered "Positive", UODB is marked as negative

## Path Nodes Dissected
```{r}
t <- pp[pp$u_pathnodes_dissected != pp$s_pathnodes_dissected,]


wrongnodes_s_u <- t %>%
  filter(!is.na(u_pathnodes_dissected)) %>%
           select(de_id, u_pathnodes_dissected, s_pathnodes_dissected, p_pathnodes_dissected)
  
t <- pp[pp$u_pathnodes_dissected != pp$p_pathnodes_dissected,]
wrongnodes_p_u <- t %>%
  filter(!is.na(u_pathnodes_dissected)) %>%
           select(de_id, u_pathnodes_dissected, p_pathnodes_dissected, p_pathnodes_dissected)


View(wrongnodes_s_u)
pp$s_pathnodes_dissected

```

- 3 cases
- row index 720
- row index 1937
- row index 1978


```{r}
t <- lapply(vars, compareqc)
t <- do.call(rbind, t)
u <- as.data.frame(t)
u$variable <- row.names(t)
row.names(u) <- NULL
u <- u[c("variable", "(n)", "(%)")]

kable(u)
```

# Looking up specific cases
```{r}

pp %>%
  filter(u_glcombined == "4+5") %>%
  filter(s_glcombined == "4+4") %>%
  select(de_id)

```